Exploring the conformational dynamics of alanine dipeptide in solution subjected to an external electric field: A nonequilibrium molecular dynamics simulation

### 2014-02-21 writedown/npt-neq/alanine.tex
small changes

@@

\subsection{System settings and simulation protocol}
The system is set up in a $2.7\times 2.7\times
2.7\, \textsf{nm}^3$ periodic simulation region, with one alanine dipeptide
described by the CHARMM27 force field, and dissolved in 644 TIP3P
water molecules.
%The EF exserts force $\vect F = q \vect E(t)$ on
%the partial charge $q$ in the system.
The size of the  dynamical region is $R_{ex} = 1.0$~nm.
All simulations are performed by a home-modified GROMACS 4.5~\cite{pronk2013gromacs}.
First, an equilibrium NVT simulation at 300~K of
100~\textsf{ns} was performed with a Langevin thermostat (time-scale
$\tau_T = 0.5~\textsf{ps}$).  Along the trajectory, configurations were taken every
50~\textsf{ps} and we used 2000 initial configurations for each nonequilibrium
MD simulation (if not stated otherwise for specific cases).
The branching trajectories were integrated by the
Leap-frog scheme with the aforementioned nonequilibrium
temperature control technique.  The
time step was $\Delta t = 0.002~\textsf{ps}$. The short-range
interaction was smoothed from $0.8$ to $1.0~\textsf{nm}$ by the
``switch'' method provided by GROMACS.  An energy conserving PME
method was applied to calculate the electrostatic interaction in this
periodic system. In the thermostated region, the original dynamics was
coupled to a Langevin thermostat with $\tau_T = 0.1~\textsf{ps}$.
  In all testing cases, this local thermostat is able to control
  the system at the desired temperature, i.e.~300~K (the results
  are not presented in this paper).
The whole system is also coupled to a Parrinello-Rahman barostat~\cite{parrinello1981polymorphic} with $\tau_P = 2.0~\textsf{ps}$ to keep
the pressure at ambient condition (1~Bar). Since the
change of the system size is small and slow, the pressure control
does not have an sizable effect on the
dynamics of the system.
At time $t=0$~ps, the system
has been fully equilibrated without any EF. From $t=0$ to
the warm-up time $t=t_{\textrm{warm}}$, the EF is switched on linearly, while
after $t=t_{\textrm{warm}}$, the field is kept constant in time at
$E_{\infty}$.  In this work we consider $t_{\textrm{warm}} = 10$~ps,
and $E_{\infty} = 1$~V/nm.
The direction of the field is arbitrarily chosen along the
$x$ direction.
In this paper we denote the
EF as a function of time $\vect E(t)$.
Therefore, for the case of constant EF, we have
$\vect E(t) = (E_\infty\cdot t/t_{warm},0,0)$ for $0\leq t < t_{warm}$, and 
$\vect E(t) = (E_\infty,0,0)$
for $t \geq t_{warm}$.

@@

\begin{figure}
  \centering
  \includegraphics[width=1.00\textwidth]{fig-all.eps}
  % \raisebox{0.2\height}{\includegraphics[width=0.22\textwidth]{c-2.eps}}
  % \includegraphics[width=0.37\textwidth]{fig-begin-1.eps}
  % \includegraphics[width=0.37\textwidth]{fig-end-1.eps}
  \caption{
    The probability density of the conformations of the alanine dipeptide plotted on the Ramachandran plot.
    (a): Two dihedral angles
    $\phi$ and $\psi$ are used to represent the molecular conformations of the alanine dipeptide.
    (b): The equilibrium probability density 
    at $t=0$~\textsf{ps}. (c): The probability density of equilibrium at $t=1000$~\textsf{ps}, resulting from the application of a constant EF of 1~V/nm. Darker color
    indicates higher probability.
    Plots are divided into 5 subregions corresponding
    to 5 molecular conformations:
    $A_1 = \{(\phi, \psi) | -134^\circ \leq \phi <  13^\circ, -125^\circ \leq \psi < 74^\circ\}$,
    $A_2 = \{(\phi, \psi) |  128^\circ \leq \phi < 226^\circ, -125^\circ \leq \psi < 74^\circ\}$,
    $B_1 = \{(\phi, \psi) | -110^\circ \leq \phi <  13^\circ,   74^\circ \leq \psi < 235^\circ\}$,
    $B_2 = \{(\phi, \psi) |  128^\circ \leq \phi < 250^\circ,   74^\circ \leq \psi < 235^\circ\}$,
    $C   = \{(\phi, \psi) |   13^\circ \leq \phi < 128^\circ, -180^\circ \leq \psi < 180^\circ\}$.
    Considering the angular periodicity, The angle, for example, $226^\circ$ corresponds to $-134^\circ$
    on the plot (b) and (c).
    % Considering the angular periodicity, if we write, for example,
    % $128^\circ \leq \phi <-134^\circ$, it implies that $\phi$ is in a range of $98$ degrees, between $128^\circ$ and $226^\circ$ ($226^\circ$ correspond to $-134^\circ$).
    This division is the same for both plot (b) and (c).
  }
  \label{fig:tmp4}
\end{figure}

@@

@@

\begin{figure}
  \centering
  \includegraphics[]{fig-meta-npt.eps}
  \caption{The time-dependent probability of conformations $P_I(t)$ 
    when a constant EF is present, where $\sum_I P_I(t) = 1, \forall t$.
    The warm-up time is $t_{warm} = 10$~ps. The red line refers to conformation $I = A_1$,
    green to $A_2$, dark blue to $B_1$, purple to $B_2$ and light blue
    to $C$. 
  }
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-1.eps}
  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-2.eps}
  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-3.eps}
  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-4.eps}
  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-5.eps}
  \caption{
    The net probability flux for the constant EF case.
    The warm-up time is $t_{warm} = 10$~ps.
    The probability flux $F_{J,I}(t)$ (defined by Eqn.~\eqref{eqn:tmp7}) is reported in units of $\textrm{ps}^{-1}$.
    From top, left to right we report $I = A_1$, $A_2$, $B_1$; bottom, left to right $B_2$ and
    $C$, respectively. In each plot, the red line stands for $J=A_1$,
    green for $J=A_2$, dark blue for $J=B_1$, purple for $J=B_2$ and light blue
    for $J=C$.
    }
  \label{fig:tmp6}
\end{figure}

@@

\begin{table}
  \centering
  \begin{tabular*}{0.4\textwidth}{@{\extracolsep{\fill}}lc}\hline\hline
    Direction        & time scale [ ps ] \\\hline
    $A_1\rightarrow A_2$        &       $\sim 10$      \\
    $B_1\rightarrow B_2$        &       $\sim 10$      \\    
    $B_2\rightarrow A_1,\ A_2,\ C$        &       $\sim 50$      \\    
    $A_2\rightarrow A_1$        &       $\sim 100$      \\
    $B_2\rightarrow B_1$        &       $\sim 100$      \\    
    $B_1\rightarrow A_1,\ C$        &       $\sim 500$      \\    \hline\hline
  \end{tabular*}
  \caption{A list of the main probability fluxes and the corresponding time scales observed in the constant EF case.}
  \label{tab:tmp1}
\end{table}

\subsection{Molecular dipole response}
The fact that our external perturbation corresponds to the action of an electric field, naturally leads to the question of how the behaviour of the electric dipole moment of the molecule is influenced by the direct interaction with EF, and, in turn, how this is related to the overall conformational behaviour of the molecule reported in the previous section.
\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{fig-dipol-order-conf.eps}
  \caption{The
    $x$-component of the molecular dipole moment, and the orientational order parameter
    of the alanine molecule as a
    function of time. The solid line represents the dipole moment,
    while the dashed line represents the orientational order parameter.
    The left vertical axis is for the dipole moment, while
    the right is for the orientational order parameter.
  }
  \label{fig:tmp3}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[]{fig-meta-conv.eps}
  \caption{Testing the finite-size effect on the dynamical and thermostated region.
    Probabilities of different conformations are presented versus time.
    See the text for more details.
  }
  \label{fig:tmp7}
\end{figure}

@@

\section{Case II:
  periodically oscillatory EF}
A step forward in our study is to consider a periodically oscillatory EF which has
a $\sin$-wave shape:
\begin{align}
  \vect E(t) = (E_0\sin(2\pi t / \period), 0, 0),
\end{align}
where $E_0$ is the intensity of the field, which is chosen to be
1.0~V/nm.  $\period$ is the oscillating period.
Here we tested three different
periods 10, 40 and 200~ps.
\begin{figure}
  \centering
  \includegraphics[width=0.48\textwidth]{fig-mode2-dipol.eps}
  \includegraphics[width=0.48\textwidth]{fig-mode2-order.eps}
  \caption{Illustration of the effect of the oscillatory EF on the system:
    (a) the dipole moment  and (b) the
    orientational order parameter of alanine dipeptide as a
    function of time. In (a),
    only the $x$-component of the dipole moment is
    shown. The black line refers to the static EF which is turned on
    at time $t_{warm} = 10$~ps. The red line refers to the oscillatory field with period of
    10~ps. The green line is of 40~ps; and the blue of 200~ps.}
  \label{fig:tmp8}
\end{figure}
Fig.~\ref{fig:tmp8} (a)
presents the $x$-component of the molecular dipole moment as
a function of time. The red, green and blue lines report the
results of $\period =10$~ps, 40~ps and 200~ps, respectively. The black line
shows the dipole moment under constant EF
for reference.
It shows that the oscillating period of the molecular dipole moment
is the same as the period of the oscillatory EF. Therefore,
the molecular dipole moment
is able to respond to the external EF almost immediately.
At $\period =200$~ps, the maximum magnitude of the molecular
dipole moment is close to the value obtained in the case of constant EF, which
means that the variation of the oscillatory EF is so slow that the
alanine has enough time to 
relax its dipole. However,
for $\period =10$ and 40~ps, the EF oscillates faster and the molecule 
does not have enough time to fully relax the dipole, as a consequence the maximum dipole moment is smaller than the previous case.
Fig.~\ref{fig:tmp9}~(b) presents the orientational order
parameter. The notations are the same as Fig~\ref{fig:tmp9}~(a).
For all cases the order parameter is much
smaller than in the case of constant EF. One possible reason is that the
relaxation of the order parameter is very slow, and the molecule in the case of oscillatory field is
not exposed to a strong enough EF for a time long enough.
For  $\period =10$ and 40~ps, the orientation of the alanine shows a weak tendency
to be parallel to the EF. It is worth to notice that for constant EF,
we also observe a quick alignment of the molecular orientation vector to the EF
on the time scale of 10~ps. For $\period =200$~ps, the molecule tends periodically
to be more perpendicular to the EF, but this directional preference is much
weaker than in the case of constant EF.

\begin{figure}
  \centering
  \includegraphics[width=0.32\textwidth]{fig-meta-mode2-0010.eps}
  \includegraphics[width=0.32\textwidth]{fig-meta-mode2-0040.eps}
  \includegraphics[width=0.32\textwidth]{fig-meta-mode2-0200.eps}
  % \includegraphics[width=0.49\textwidth]{fig-meta-mode2-2000.eps}
  \caption{The probability of being in a given of conformation for alanine in a   periodically oscillatory EF. Different periods,
    i.e. $\period =10$~ps, 40~ps and 200~ps, are considered here.  The
    probability of being in a certain conformation $I$, which is
    denoted by $P_I$ in this paper, is plotted by colored lines against
    time. Red line: $I = A_1$,  green line: $I = A_2$,  dark
    blue line: $I = B_1$,  pink line: $I = B_2$ and  light blue
    line: $I = C$. For $\period =10$~ps and 40~ps, the nonequilibrium
    simulations last 1000~ps, while for $\period =200$~ps,
    they last 6400~ps.  }
  \label{fig:tmp9}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-5.eps}\\
  \caption{
    Integrated probability flux $Q_{J,I}(t)$ for the periodically
    oscillatory EF, is plotted against time (horizontal axis, in picoseconds).
    The integrated
    probability flux is defined by $Q_{J,I}(t) = \int_0^t F_{J,I}(\tau) d\tau$, where
    $F_{J,I}(t)$ is the net probability flux from conformation $J$ to $I$.
    See also Eqn.~\eqref{eqn:tmp7} and~\eqref{eqn:tmp7a} for definitions
    of $F_{J,I}(t)$ and $Q_{J,I}(t)$, respectively.
    From top to bottom, rows report results with  period 10, 40 and 200~ps, respectively.
    From left to right, the five
    columns show the integrated flux $Q_{J,A_1}$, $Q_{J,A_2}$,
    $Q_{J,B_1}$, $Q_{J,B_2}$ and $Q_{J,C}$, respectively. In each plot,
    the red line stands for $J=A_1$, green for $J=A_2$, dark blue for $J=B_1$,
    purple for $J=B_2$ and light blue for $J=C$.
    An increasing value of $Q_{J,I}$ indicates a net probability
      flux from conformation $J$ to $I$,
      while a decreasing value of $Q_{J,I}$ indicates a net probability
      flux from $I$ to $J$.
  }
  \label{fig:tmp10}
\end{figure}

>>>>

\recheck{ The proposed temperature control method is very similar to
  the stochastic boundary condition proposed by Brooks~III and Karplus~\cite{brooks1983deformable}.
  The only difference is that we do not explicitly consider a boundary
  region: The system that is divided into a dynamical region (reaction region in their paper) and
  a thermostated regoin (stochastic buffer region in their paper)
  is put into a 3-D cubic periodic simulation box.
}

@@

\subsection{System settings and simulation protocol}
The system is set up in a $2.7\times 2.7\times
2.7\, \textsf{nm}^3$ periodic simulation region, with one alanine dipeptide
described by the CHARMM27 force field~\cite{foloppe2000all}, and dissolved in 644 TIP3P~\cite{jorgensen1983comparison}
water molecules.  \recheck{The grid-based energy correction map (CMAP)~\cite{mackerell2004extending}
for the backbone dihedral angles is also taken into consider.}
%The EF exserts force $\vect F = q \vect E(t)$ on
%the partial charge $q$ in the system.
The size of the  dynamical region is $R_{ex} = 1.0$~nm.
All simulations are performed by a home-modified GROMACS~4.5~\cite{pronk2013gromacs} with support to the CHARMM
force field~\cite{bjelkmar2010implementation}.
First, an equilibrium NVT simulation at 300~K of
100~\textsf{ns} was performed with a Langevin thermostat (time-scale
$\tau_T = 0.5~\textsf{ps}$).  Along the trajectory, configurations were taken every
50~\textsf{ps} and we used 2000 initial configurations for each nonequilibrium
MD simulation (if not stated otherwise for specific cases).
The branching trajectories were integrated by the
Leap-frog scheme with the aforementioned nonequilibrium
temperature control technique.  The
time step was $\Delta t = 0.002~\textsf{ps}$.
\recheck{The short-range
interaction (van der Waals interaction)
had the cut-off radius of 1.0~nm, and was smoothed from $0.8$ to $1.0$~nm by the
``switch'' method provided by GROMACS.
A energy conserving particle mesh Ewald method (PME)~\cite{darden1993pme, essmann1995spm}
method was applied to calculate the electrostatic interaction in this
periodic system. The the direct space part of PME was cut-offed and smoothed in the
same way as the van der Waals interaction.}
\recheck {All hydrogen involving bonds are constrained by LINCS~\cite{hess1997lincs}, expect that
  the TIP3P water molecules are constrained by SETTLE algorithm~\cite{miyamoto2004settle}.}
In the thermostated region, the original dynamics was
coupled to a Langevin thermostat with $\tau_T = 0.1~\textsf{ps}$.
  In all testing cases, this local thermostat is able to control
  the system at the desired temperature, i.e.~300~K (the results
  are not presented in this paper).
The whole system is also coupled to a Parrinello-Rahman barostat~\cite{parrinello1981polymorphic} with $\tau_P = 2.0~\textsf{ps}$ to keep
the pressure at ambient condition (1~Bar). Since the
change of the system size is small and slow, the pressure control
does not have an sizable effect on the
dynamics of the system.
At time $t=0$~ps, the system
has been fully equilibrated without any EF. From $t=0$ to
the warm-up time $t=t_{\textrm{warm}}$, the EF is switched on linearly, while
after $t=t_{\textrm{warm}}$, the field is kept constant in time at
$E_{\infty}$.  In this work we consider $t_{\textrm{warm}} = 10$~ps,
and $E_{\infty} = 1$~V/nm.
The direction of the field is arbitrarily chosen along the
$x$ direction.
In this paper we denote the
EF as a function of time $\vect E(t)$.
Therefore, for the case of constant EF, we have
$\vect E(t) = (E_\infty\cdot t/t_{warm},0,0)$ for $0\leq t < t_{warm}$, and 
$\vect E(t) = (E_\infty,0,0)$
for $t \geq t_{warm}$.

@@

\begin{figure}
  \centering
  \includegraphics[width=1.00\textwidth]{fig-all.eps}
  % \raisebox{0.2\height}{\includegraphics[width=0.22\textwidth]{c-2.eps}}
  % \includegraphics[width=0.37\textwidth]{fig-begin-1.eps}
  % \includegraphics[width=0.37\textwidth]{fig-end-1.eps}
  \caption{
    The probability density of the conformations of the alanine dipeptide plotted on the Ramachandran plot.
    (a): Two dihedral angles
    $\phi$ and $\psi$ are used to represent the molecular conformations of the alanine dipeptide.
    (b): The equilibrium probability density 
    at $t=0$~\textsf{ps}. (c): The probability density of equilibrium at $t=1000$~\textsf{ps}, resulting from the application of a constant EF of 1~V/nm. Darker color
    indicates higher probability.
    Plots are divided into 5 subregions corresponding
    to 5 molecular conformations:
    $A_1 = \{(\phi, \psi) | -134^\circ \leq \phi <  13^\circ, -125^\circ \leq \psi < 74^\circ\}$,
    $A_2 = \{(\phi, \psi) |  128^\circ \leq \phi < 226^\circ, -125^\circ \leq \psi < 74^\circ\}$,
    $B_1 = \{(\phi, \psi) | -110^\circ \leq \phi <  13^\circ,   74^\circ \leq \psi < 235^\circ\}$,
    $B_2 = \{(\phi, \psi) |  128^\circ \leq \phi < 250^\circ,   74^\circ \leq \psi < 235^\circ\}$,
    $C   = \{(\phi, \psi) |   13^\circ \leq \phi < 128^\circ, -180^\circ \leq \psi < 180^\circ\}$.
    Considering the angular periodicity, the angle, for example, $226^\circ$ corresponds to $-134^\circ$
    on the plot (b) and (c).
    % Considering the angular periodicity, if we write, for example,
    % $128^\circ \leq \phi <-134^\circ$, it implies that $\phi$ is in a range of $98$ degrees, between $128^\circ$ and $226^\circ$ ($226^\circ$ correspond to $-134^\circ$).
    This division is the same for both plot (b) and (c).
  }
  \label{fig:tmp4}
\end{figure}

@@

\recheck{ The definition of the probability flux is similar to the
  kinetic rate.  However, we want to stress that, in genarl, the
  probability flux should not be interpreted as a kinetic rate, and
  one cannot replace the nonequilibrium molecular dynamics by a
  kinetic analysis. The main reason is that the conformational
  dynamics of alanine dipeptide is generally not Markovian for a small
  time interval $\Delta t$~\cite{prinz2011markov}, therefore, a direct application of the kinetic
  analysis is questionable. Since the main goal of our research is to propose a
  nonequilibrium molecular dynamics simulation method, the numerical
  results will not be compared with a kinetic analysis.
}

@@

\begin{figure}
  \centering
  \includegraphics[]{fig.ala.new/fig-meta-npt.eps}
  \caption{The time-dependent probability of conformations $P_I(t)$ 
    when a constant EF is present, where $\sum_I P_I(t) = 1, \forall t$.
    The warm-up time is $t_{warm} = 10$~ps. The red line refers to conformation $I = A_1$,
    green to $A_2$, dark blue to $B_1$, purple to $B_2$ and light blue
    to $C$. 
  }
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-1.eps}
  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-2.eps}
  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-3.eps}
  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-4.eps}
  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-5.eps}
  \caption{
    The net probability flux for the constant EF case.
    The warm-up time is $t_{warm} = 10$~ps.
    The probability flux $F_{J,I}(t)$ (defined by Eqn.~\eqref{eqn:tmp7}) is reported in units of $\textrm{ps}^{-1}$.
    From top, left to right we report $I = A_1$, $A_2$, $B_1$; bottom, left to right $B_2$ and
    $C$, respectively. In each plot, the red line stands for $J=A_1$,
    green for $J=A_2$, dark blue for $J=B_1$, purple for $J=B_2$ and light blue
    for $J=C$.
    }
  \label{fig:tmp6}
\end{figure}

@@

\begin{table}
  \centering
  \begin{tabular*}{0.4\textwidth}{@{\extracolsep{\fill}}lc}\hline\hline
    Direction        & time scale [ ps ] \\\hline
    $A_1\rightarrow A_2$        &       $\sim 10$      \\
    % $B_1\rightarrow B_2$        &       $\sim 10$      \\    
    $B_2\rightarrow A_1,\ A_2,\ C$        &       $\sim 50$      \\    
    $A_2\rightarrow A_1$        &       $\sim 100$      \\
    $B_2\rightarrow B_1$        &       $\sim 100$      \\    
    $B_1\rightarrow A_1,\ C$        &       $\sim 500$      \\    \hline\hline
  \end{tabular*}
  \caption{A list of the main probability fluxes and the corresponding time scales observed in the constant EF case.}
  \label{tab:tmp1}
\end{table}

\subsection{Molecular dipole response}
The fact that our external perturbation corresponds to the action of
an electric field, naturally leads to the question of how
\recheck{
  the molecular dipole aligns along the direction of external EF}, and, in turn, how this is related
to the overall \recheck{conformational selection} of the molecule reported in
the previous section.
\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{fig.ala.new/field.dipole/fig-dipol-order-conf.eps}
  \caption{The
    $x$-component of the molecular dipole moment, and the orientational order parameter
    of the alanine molecule as a
    function of time. The solid line represents the dipole moment,
    while the dashed line represents the orientational order parameter.
    The left vertical axis is for the dipole moment, while
    the right is for the orientational order parameter.
  }
  \label{fig:tmp3}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[]{fig.ala.new/fig-meta-conv.eps}
  \caption{Testing the finite-size effect on the dynamical and thermostated region.
    Probabilities of different conformations are presented versus time.
    See the text for more details.
  }
  \label{fig:tmp7}
\end{figure}

@@

\section{Case II:
  periodically oscillatory EF}
A step forward in our study is to consider a periodically oscillatory EF which has
a $\sin$-wave shape:
\begin{align}
  \vect E(t) = (E_0\sin(2\pi t / \period), 0, 0),
\end{align}
where $E_0$ is the intensity of the field, which is chosen to be
1.0~V/nm.  $\period$ is the oscillating period.
Here we tested three different
periods 10, 40 and 200~ps.
\begin{figure}
  \centering
  \includegraphics[width=0.48\textwidth]{fig.ala.new/fig-mode2-dipol.eps}
  \includegraphics[width=0.48\textwidth]{fig.ala.new/fig-mode2-order.eps}
  \caption{Illustration of the effect of the oscillatory EF on the system:
    (a) the dipole moment  and (b) the
    orientational order parameter of alanine dipeptide as a
    function of time. In (a),
    only the $x$-component of the dipole moment is
    shown. The black line refers to the static EF which is turned on
    at time $t_{warm} = 10$~ps. The red line refers to the oscillatory field with period of
    10~ps. The green line is of 40~ps; and the blue of 200~ps.}
  \label{fig:tmp8}
\end{figure}
Fig.~\ref{fig:tmp8} (a)
presents the $x$-component of the molecular dipole moment as
a function of time. The red, green and blue lines report the
results of $\period =10$~ps, 40~ps and 200~ps, respectively. The black line
shows the dipole moment under constant EF
for reference.
It shows that the oscillating period of the molecular dipole moment
is the same as the period of the oscillatory EF. Therefore,
the molecular dipole moment
is able to respond to the external EF almost immediately.
At $\period =200$~ps, the maximum magnitude of the molecular
dipole moment is close to the value obtained in the case of constant EF, which
means that the variation of the oscillatory EF is so slow that the
alanine has enough time to 
relax its dipole. However,
for $\period =10$ and 40~ps, the EF oscillates faster and the molecule 
does not have enough time to fully relax the dipole, as a consequence the maximum dipole moment is smaller than the previous case.
Fig.~\ref{fig:tmp9}~(b) presents the orientational order
parameter. The notations are the same as Fig~\ref{fig:tmp9}~(a).
For all cases the order parameter is much
smaller than in the case of constant EF. One possible reason is that the
relaxation of the order parameter is very slow, and the molecule in the case of oscillatory field is
not exposed to a strong enough EF for a time long enough.
For  $\period =10$ and 40~ps, the orientation of the alanine shows a weak tendency
to be parallel to the EF. It is worth to notice that for constant EF,
we also observe a quick alignment of the molecular orientation vector to the EF
on the time scale of 10~ps. For $\period =200$~ps, the molecule tends periodically
to be more perpendicular to the EF, but this directional preference is much
weaker than in the case of constant EF.

\begin{figure}
  \centering
  \includegraphics[width=0.32\textwidth]{fig.ala.new/fig-meta-mode2-0010.eps}
  \includegraphics[width=0.32\textwidth]{fig.ala.new/fig-meta-mode2-0040.eps}
  \includegraphics[width=0.32\textwidth]{fig.ala.new/fig-meta-mode2-0200.eps}
  % \includegraphics[width=0.49\textwidth]{fig-meta-mode2-2000.eps}
  \caption{The probability of being in a given of conformation for alanine in a   periodically oscillatory EF. Different periods,
    i.e. $\period =10$~ps, 40~ps and 200~ps, are considered here.  The
    probability of being in a certain conformation $I$, which is
    denoted by $P_I$ in this paper, is plotted by colored lines against
    time. Red line: $I = A_1$,  green line: $I = A_2$,  dark
    blue line: $I = B_1$,  pink line: $I = B_2$ and  light blue
    line: $I = C$. For $\period =10$~ps and 40~ps, the nonequilibrium
    simulations last 1000~ps, while for $\period =200$~ps,
    they last 6400~ps.  }
  \label{fig:tmp9}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0010-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0010-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0010-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0010-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0010-iflux-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0040-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0040-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0040-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0040-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0040-iflux-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0200-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0200-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0200-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0200-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0200-iflux-5.eps}\\
  \caption{
    Integrated probability flux $Q_{J,I}(t)$ for the periodically
    oscillatory EF, is plotted against time (horizontal axis, in picoseconds).
    The integrated
    probability flux is defined by $Q_{J,I}(t) = \int_0^t F_{J,I}(\tau) d\tau$, where
    $F_{J,I}(t)$ is the net probability flux from conformation $J$ to $I$.
    See also Eqn.~\eqref{eqn:tmp7} and~\eqref{eqn:tmp7a} for definitions
    of $F_{J,I}(t)$ and $Q_{J,I}(t)$, respectively.
    From top to bottom, rows report results with  period 10, 40 and 200~ps, respectively.
    From left to right, the five
    columns show the integrated flux $Q_{J,A_1}$, $Q_{J,A_2}$,
    $Q_{J,B_1}$, $Q_{J,B_2}$ and $Q_{J,C}$, respectively. In each plot,
    the red line stands for $J=A_1$, green for $J=A_2$, dark blue for $J=B_1$,
    purple for $J=B_2$ and light blue for $J=C$.
    An increasing value of $Q_{J,I}$ indicates a net probability
      flux from conformation $J$ to $I$,
      while a decreasing value of $Q_{J,I}$ indicates a net probability
      flux from $I$ to $J$.
  }
  \label{fig:tmp10}
\end{figure}

Fig.~\ref{fig:tmp9} shows the probability of the
conformations against time for periodically oscillatory EF,
while  
Fig.~\ref{fig:tmp10} presents the integrated net probability fluxes
(defined by Eqn.~\eqref{eqn:tmp7a}) between
conformations. Here the probability fluxes are not reported
because the profiles are highly oscillating and they would not offer 
a better information than the one that can be obtained from the integrated probability flux.
Coming back to Fig.~\ref{fig:tmp9}, for all periods investigated,
the observed time-dependent probabilities  in $A_1$, $A_2$, $B_1$ and $B_2$ are
highly oscillating and the average value over time cycles does not change
considerably w.r.t.~time.
However, the probability in conformation $C$ significantly
increases to approximately 0.17 for $\period =10$~ps, 0.27 for  $\period =40$~ps, and
0.26 for $\period =200$~ps.
In the case of $\period =10$ and $40$~ps, {the probability of conformation $C$}
reaches the steady value in around 300~ps, while it requires about 1200~ps
for the $\period =200$~ps case. 
The notable increment of probability of $A_1$ and
  the vanishing of $B_1$ in the constant EF case (see Fig.~\ref{fig:tmp5})
are not observed in the oscillatory EF case.
\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{graph-t0010-2.eps}
  \caption{Schematic plot of the main probability flux between conformations
    for periodically oscillatory EF, $\period =10$~ps. The thickness 
    of the arrows approximately presents the strength of the flux.
    The numbers near the arrows indicates the strength of the averaged
    probability flux, the unit of which is $10^{-3}\times\textrm{ps}^{-1}$.
  }
  \label{fig:tmp11}
\end{figure}
In comparison to the static EF case, where the probability flux
vanishes when the system reaches steady state (Fig.~\ref{fig:tmp6}), 
Fig.~\ref{fig:tmp10} shows increasing
integrated probability net fluxes, which imply some lasting and directional
fluxes among the conformations (see Fig.~\ref{fig:tmp9}).
Fig.~\ref{fig:tmp11} presents
a schematic plot of the main probability fluxes for $\period =10$~ps.
The thickness of the arrows and the numbers nearby indicate
the steady value of average net fluxes over periods.
{
The relevance of Fig.~\ref{fig:tmp11} is in the fact that it suggests,
in perspective, a general scenario common to all molecules
characterized by $\beta$-sheet-like or $\alpha$-helix-like
conformations and how an electric field is likely to modify it.
}
The probability flux of $\period =40$~ps is quantitatively
comparable to the case $\period =10$~ps, except that the probability fluxes
going into conformation $C$ is stronger, which actually results in
a higher steady probability in $C$.
The probability flux of case $\period =200$~ps is qualitatively
similar to $\period =10$~ps and $\period =40$~ps, however,
the strength is much lower than the latter two cases.
Moreover, 
  we see that the integrated fluxes $Q_{A_2,A_1}$ and $Q_{B_1,A_2}$ reach
  a steadily
increasing stage after about 3200~ps, which is even longer than the time scale
at which the probability of $C$ reaches its steady value. This indicates
a longer intrinsic time scale in the $\period =200$~ps case.
